---
title: "HuaYangProblemsSet3"
author: "Hua Yang"
date: "2022-10-21"
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GBA 5140 Statistics Essentials for Business Analytics
## Problem Set 3
## Probability Distribution


Problem 1
Automobile repair costs continue to rise with the average cost now at $367 per repair (U.S. News & World Report website, January 5, 2015). Assume that the cost for an automobile repair is normally distributed with a standard deviation of $88. Write R code to achieve the following tasks. Post your R code and RStudio output (console output) below each task.

 ```{r }
```

**1.What is the probability that the cost will be more than $450?**
```{r mtcars_df}
print(paste("the probability that the cost will be more than $450: ",pnorm(450,mean=367,sd=88,lower.tail = FALSE)))
```

**2.What is the probability that the cost will be less than $250?**

```{r }
print(paste("the probability that the cost will be less than $250: ",pnorm(250,mean=367,sd=88)))
```

 

**3.What is the probability that the cost will be between $250 and $450?**

```{r}
print(paste("the probability that the cost will be between $250 and $450: ",pnorm(450,mean=367,sd=88)-pnorm(250,mean=367,sd=88)))
```

 

**4.If the cost of your car repair is in the lower 5% of automobile repair charges, what is your cost?**
```{r}
print(paste("If the cost of your car repair is in the lower 5% of automobile repair charges, cost: ",qnorm(0.05,mean=367,sd=88)))
```

